\section{Approach}

% This section should include a description of our technology / approach.
% This is the technology-related section.

We plan to conduct a survey across crowds that gauges their views on various aspects of web pages of applications. We control for differences in application cost by only examining free applications.
We will scrape about 500 applications and get about 5000 participants to do the survey (Our sample must be big to offset random error.).
We plan to use Android apps since its application marketplace publicly provides download statistics, albeit in discretized increments.
We plan to examine a specific subset of apps: games + productivity app (The use of games is discretionary, so we must also examine something else that people need to use). \\

We will incentivize users by making the study fun to complete. If not enough users complete the study in this way, we will proceed to obtain some users via Mechanical Turk.
setup: quick survey + first batch of 5
We plan to show applications in different orders to different people (to eliminate systematic biases).
We will try to have roughly the same distribution of dates for when the applications were released.
We plan to separate applications into 2 categories: (1) relatively new to the market, so users have not seen them before, and (2) been in the market for a while
show mock-up of application store listing (all must be the same except for the variable being tested) if Android releases information on older applications.
To obtain data, we plan to scrape the names, icons, and descriptions of the aforementioned applications.
