\section{Approach}

In order to tackle this problem we will perform the following: We intend to scrape 500 mobile game applications from the Android market. We are aiming for a total of 5000 participants for our study. For each trial, a subject will be asked to compare two factors within two applications.  These factors are the following: (1) which application will be more successful and (2) why. The user will be only shown the titles and icons of the apps for five\?\? seconds. During the trials, users will be asked to briefly explain their selections. We plan to issue the trials in batches of five, but we will ask users whether they have seen the application before and discard that sample if they say they have. We hope that the client-side randomization applications shown will reduce the chance of users seeing the same application multiple times. The survey will be powered by Django and a MySQL database.\\

We will make our trials more appealing by treating each trial as a test of how good users' entrepreneurial guts are. After users answer which application they think is more successful, our system will show them the real answer and ask them the reason they chose a certain option. We hope that the gamification of this experiment will lead to more users willing to participate in our survey and more experimental data to choose from. Subjects will also see a score denoting what proportion of trials they guessed correctly. We will do this through an iterative process, informing the user at each step what their score is to create a sort of competitive environment.\\

Afterwards, we will use an algorithm to rank the applications based on which ones users found to be more successful. We will see how well these rankings correlate with how successful the apps actually are in terms of download counts.

%\begin{itemize}
%HOW GOOD IS YOUR ENTREPRENEURIAL GUT?
%agreement to statement of privacy
%two name of apps + their icons
%option to opt-out if they've already seen app
%which one do you think is more successful? (select one)
%why do you think this one is more successful? (free-form comment)
%result of whether they were right or wrong + score + try again!

%\item Control for difference in application cost by only using free applications
%\item Obtain approximately 500 mobile applications and 5000 participants 
%\item Utilize the application store: Preference towards Androids since they publicly provide download statistics
%\item Use samples from games and productivity applications
%\item Incentivize users by making the study fun to complete and additionally taking advantage of users from Mechanical Turk to cover the remaining numbers required.
%\item Performing a quick survey for the first five users
%\item Display applications in different orders to weed out systematic preferences based on order.
%\item Utilizing apps with roughly the same distribution of dates of release
%\item Separating applications into two categories: (1) relatively new to the market, so users have not seen them before, and (2) been in the market for a while
%\item Displaying a mock-up of the application store listing (all must be the same except for the variable being tested)
%\item Scaping the the names, icons, and descriptions of the aforementioned applications from the Android store
%\end{itemize}
%
%We plan to conduct a survey across crowds that gauges their views on various aspects of web pages of applications. We control for differences in application cost by only examining free applications.
%We will scrape about 500 applications and get about 5000 participants to do the survey (Our sample must be big to offset random error.).
%We plan to use Android apps since its application marketplace publicly provides download statistics, albeit in discretized increments.
%We plan to examine a specific subset of apps: games + productivity app (The use of games is discretionary, so we must also examine something else that people need to use). \\
%
%We will incentivize users by making the study fun to complete. If not enough users complete the study in this way, we will proceed to obtain some users via Mechanical Turk.
%setup: quick survey + first batch of 5
%We plan to show applications in different orders to different people (to eliminate systematic biases).
%We will try to have roughly the same distribution of dates for when the applications were released.
%We plan to separate applications into 2 categories: (1) relatively new to the market, so users have not seen them before, and (2) been in the market for a while
%show mock-up of application store listing (all must be the same except for the variable being tested) if Android releases information on older applications.
%To obtain data, we plan to scrape the names, icons, and descriptions of the aforementioned applications.
